\bf\mftitle

### 2011-03-02 doc/jInfer/tutorials/building_jinfer.tex
minor to building, tutorial_dev is OK
last minute corrections + PDF

\par 
  This document assumes that your computer is set to use jInfer, meaning you
    have correct version of NetBeans installed and you can run jInfer.

\subsection*{Getting jInfer sources}
\par 
There are two main ways of obtaining jInfer source files: from a version
  distribution, or from the Subversion repository. The first way might be more
  convenient and secure (version distributions are usually more stable than the
  bleeding edge code in repository), however you might prefer to build the
  latest code.

\par 
  The first way, obtaining sources from version distribution:

\begin{enumerate}\item 
 Go to \url{https://sourceforge.net/projects/jinfer/files/}.
  \item Download the latest jInfer sources (jInfer-X.Y-src.zip).
  \item Unpack the ZIP, you'll get a few directories. One of them will be \texttt{src}.
  \item Continue by building jInfer.
  \end{enumerate}
\par 
  Second way, checking out Subversion repository: you will need a
  Subversion client, such as the command line client or TortoiseSVN. In any case,
  \url{http://subversion.apache.org/}
might be a good place to start. To check out
  jInfer, use the following URL:
  \url{https://jinfer.svn.sourceforge.net/svnroot/jinfer}.
  After the checkout, continue by building jInfer.

\subsection*{Building from NetBeans}
\par 
  This is perhaps the easier, more user friendly way of building jInfer.
    If you however wish to automate the building process, you might want to
    try using Ant - in that case, see the next section.

>>>>

\par 
  This document assumes that your computer is set to use jInfer, meaning you
    have the correct version of NetBeans installed and you can run jInfer.

\subsection*{Getting jInfer sources}
\par 
There are two main ways for obtaining jInfer source files: from a version
  distribution, or from the Subversion repository. The first way might be more
  convenient and secure (version distributions are usually more stable than the
  bleeding edge code in repository), however you might prefer to build the
  latest code.

\par 
\noindent   The first way, obtaining sources from version distribution:
\begin{enumerate}\item 
 Go to \url{https://sourceforge.net/projects/jinfer/files/}.
  \item Download the latest jInfer sources (jInfer-X.Y-src.zip).
  \item Unpack the ZIP, you'll get a few directories. One of them will be \texttt{src}.
  \item Continue by building jInfer.
  \end{enumerate}
\par 
  Second way, by checking out Subversion repository: you will need a
  Subversion client, such as the command line client or TortoiseSVN. In any case,
  \url{http://subversion.apache.org/}
might be a good place to start. To check out
  jInfer, use the following URL:
  \url{https://jinfer.svn.sourceforge.net/svnroot/jinfer}.
  After the checkout, continue by building jInfer.

\subsection*{Building from NetBeans}
\par 
  This is perhaps an easier, more user friendly way of building jInfer.
    If you however wish to automate the building process, you might want to
    try using Ant - in that case, see the next section.
